---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dendrogreif

<!-- badges: start -->
<!-- badges: end -->

The goal of dendrogreif is to provide an R interface for downloading data from DendroGreif network, containing 1000+ environmental (100+ Temperature and Relative Humidity) and 500+ tree physiological sensor streams (350+ dendrometers). Currently the database is meant for the internal use, but could be opened up to the public if there is enough interest. 

## Installation

You can install the development version of dendrogreif like so:

```r
install.packages("remotes")
remotes::install_github('smiljanicm/dendrogreif')
```

You will need credentials file for the database access. Please contact marko.smiljanic@uni-greifswald.de for the access rights.

## Example

Common workflow entails looking up the site id from the sites database, getting either all or some locations from it and at the end getting the relevant data series. 

```{r example, message=FALSE}
library(dendrogreif)

## initialize database connection from credentials file.
conn <- con_init("creds")

#list all sites in the database
list_sites(conn)

#list all locations for a single site
demmin_locations <- list_locations(conn, 6)
demmin_locations %>% head(20) %>% knitr::kable()
#get single tree dendrometer
data_ind <- get_data(conn, location_ids = 67, variable_ids = 1)
print(head(data_ind))

#get all dendrometer series from the single site
data_all_dend <- get_data(conn, location_ids = get_locations(conn, site_ids=6), variable_ids = 1)
print(head(data_all_dend))

#get all series from the single site
loc_ids <- get_locations(con = conn, site_ids=6)
var_ids <- get_variables(con = conn , location_ids = loc_ids)
data_all <- get_data(conn, location_ids = loc_ids, variable_ids = var_ids)
print(head(data_all))
```
